Real-Time Scheduling Algorithms and Battery Consumption of Mobile Devices

### 2017-03-19 paper-RMDON.tex
ordenando bibliografia alfabeticamente. Generando nuevo pdf
Agregando referencias de real-time & scheduling

>>>>

\bibitem{audsley-burns-davis-tindell-wellings}N.~Audsley, A.~Burns, R.~Davis, K.~Tindell and A.~Wellings, \emph{Real-time system scheduling}, 1995 Predictably Dependable Computing Systems, Springer Berlin Heidelberg, pp. 41-52.

\bibitem{davis-burns}R.~Davis and A.~Burns, \emph{A survey of hard real-time scheduling for multiprocessor systems}, 2011 ACM computing surveys (CSUR), 43(4), 35.

\bibitem{guan-yi-gu-deng-yu}N.~Guan, W.~Yi, Z.~Gu, Q.~Deng and G.~Yu, \emph{New schedulability test conditions for non-preemptive scheduling on multiprocessor platforms}, 2008 Real-Time Systems Symposium, 2008. pp. 137-146. IEEE.

\bibitem{takada-sakamura} H.~Takada and K.~Sakamura, \emph{Real-time synchronization protocols with abortable critical sections}. 1994 Proceedings of 1st International Workshop on Real-time Computing Systems & Application, pp. 48-52
